Classification of RDF Constraint Types to Ensure High Quality of Metadata and Data

### 2015-04-28 paper/paper7/paper7.tex
introduction

The \textbf{contribution} of this paper is the development of a system 
(1) to classify RDF constraints (according to their severity levels) to evaluate the quality of (meta)data which may be represented by any vocabulary and 
(2) to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements.
By defining a huge amount of constraints of the majority of constraint types
to validate data sets from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences},  
%we apply the developed classification system to several and different vocabularies from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} in order to
we prove the claim that the developed classification system perfectly applies vocabulary-independent and therefore to prove its generality.

We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding 
(1) which sets of constraint types (on different levels of complexity) and 
(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations.

@@

The \textbf{contribution} of this paper is the development of a system 
\begin{enumerate}
	\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
\end{enumerate}
By defining a huge amount of constraints of the majority of the constraint types,   
we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).

We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding 
(1) which sets of constraint types (on different levels of complexity) and 
(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

>>>>

The \textbf{contribution} of this paper is the development of a system 
(1) to classify RDF constraints (according to their severity levels) to evaluate the quality of (meta)data which may be represented by any vocabulary and 
(2) to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements.
By defining a huge amount of constraints of the majority of constraint types
to validate data sets from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences},  
%we apply the developed classification system to several and different vocabularies from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} in order to
we prove the claim that the proposed classification system perfectly applies vocabulary-independent and therefore we prove its generality.

We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
(1) which sets of constraint types (on different levels of complexity) and 
(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations.

@@

The \textbf{contribution} of this paper is the development of a system 
\begin{enumerate}
	\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
\end{enumerate}
By defining a huge amount of constraints of the majority of the constraint types,   
we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
(1) which sets of constraint types (on different levels of complexity) and 
(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
